### 2013-02-16 doc/icml2013/algo.tex
edit

% Full algorithm
Now we are ready to state our full algorithm, which we call Spectral Experts
(\algorithmref{sec:algo}).
First, we perform three regressions to recover the compound parameters
$M_1$ \refeqn{y1},
$M_2$ \refeqn{y2}, and
$M_3$ \refeqn{y3}.
Since $M_2$ and $M_3$ both only have rank $k$,
we can use nuclear norm regularization
\cite{Tomioka2011,NegahbanWainwright2009}
to exploit this low-rank structure and improve our compound parameter estimates.
In the algorithm, the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$
are set to $\frac{1}{\sqrt{n}}$.
The resulting semidefinite program is a standard one which has received
much attention in recent years.
We use a rather simple gradient-based approach,
where the nuclear norm is handled in closed form by taking an SVD
and soft-thresholding the eigenvalues \cite{donoho95soft,cai10soft}.

@@

% Spectral
In recent years, there has a been substantial interest in ``spectral'' methods
for learning latent-variable models.  One line of work has
focused on observable operator models \cite{hsu09spectral}
in which the true parameters are not recovered, but a reparametrization is used
which enables prediction.
Another line of work is based on the method of moments and uses eigendecomposition of a certain tensor
to recover the parameters \cite{anandkumar12moments,anandkumar12svd,AnandkumarHsuKakade2012}.
Our work extends this line of work into the space of discriminative models,
which requires regression to obtain the desired tensor.

% Unmixing
In spirit, Spectral Experts also bears some resemblance to the unmixing
algorithm for estimation of restricted PCFGs
\cite{hsu12identifiability}.
In that work, the observations (moments) provided a linear combination over
the compound parameters.  ``Unmixing'' involves solving for the compound
parameters by inverting a mixing matrix.  In this work,
each data point (appropriately transformed) provides a noisy slice of the
compound parameters; retrieving the compound parameters is more involved.

% Signal
The idea of performing low-rank regression on $y^2$ has been explored
in the context of signal recovery from magnitude measurements
\cite{candes11phaselift,ohlsson12phase}.
There, the actual observed response was $y^2$,
whereas in our case, we deliberately construct powers $y,y^2,y^3$
to identify the parameters.

>>>>

% Full algorithm
Now we are ready to state our full algorithm, which we call Spectral Experts
(\algorithmref{sec:algo}).
First, we perform three regressions to recover the compound parameters
$M_1$ \refeqn{y1},
$M_2$ \refeqn{y2}, and
$M_3$ \refeqn{y3}.
Since $M_2$ and $M_3$ both only have rank $k$,
we can use nuclear norm regularization
\cite{Tomioka2011,NegahbanWainwright2009}
to exploit this low-rank structure and improve our compound parameter estimates.
In the algorithm, the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$
are set to $\frac{c}{\sqrt{n}}$ for some constant $c$.
The resulting semidefinite program is a standard one which has received
much attention in recent years.
We use a rather simple proximal gradient-based approach,
in which the nuclear norm is handled in closed form by taking an SVD
and soft-thresholding the singular values \cite{donoho95soft,cai10soft}.

@@

% Spectral
In recent years, there has a been substantial interest in ``spectral'' methods
for learning latent-variable models.  One line of work has
focused on observable operator models \cite{hsu09spectral}
in which the true parameters are not recovered, but a reparametrization is used
which enables prediction.
Another line of work is based on the method of moments and uses eigendecomposition of a certain tensor
to recover the parameters \cite{anandkumar12moments,anandkumar12svd,AnandkumarHsuKakade2012}.
Our work extends this second line into the space of discriminative models,
which requires regression to obtain the desired tensor to factorize.

% Unmixing
In spirit, Spectral Experts bears some resemblance to the unmixing
algorithm for estimation of restricted PCFGs
\cite{hsu12identifiability}.
In that work, the observations (moments) provided a linear combination over
the compound parameters.  ``Unmixing'' involves solving for the compound
parameters by inverting a mixing matrix.  In this work,
each data point (appropriately transformed) provides a different noisy projection of
the compound parameters.

% Signal
The idea of performing low-rank regression on $y^2$ has been explored
in the context of signal recovery from magnitude measurements
\cite{candes11phaselift,ohlsson12phase}.
There, the actual observed response was $y^2$,
whereas in our case, we deliberately construct powers $y,y^2,y^3$
to identify the underlying parameters.
